r5r: Rapid Realistic Routing with R5 in R

### 2020-09-18 r-package/paper2020/paper2020.Rmd
updates package download command in paper

The package can be installed with the following command:

```{r, message = FALSE, eval = FALSE}
devtools::install_github("ipeaGIT/r5r", subdir = "r-package")
```

@@

Note that the resulting `ttm` object only holds the travel time of 1043 
origin/destination pairs, even though the `points` data set passed both to 
`origins` and `destinations` argument contains 100 points. This is because out 
of the total 10000 possible trips between the supplied points, only 1043 could 
be completed within the specified restrictions. Removing any walking distance 
limits (by setting it to infinite) and increasing maximum trip duration 
accordingly results in a "complete" output?

>>>>

The package can be installed with the following commands:

```{r, message = FALSE, eval = FALSE}
# stable version
install.packages("r5r")

# development version
devtools::install_github("ipeaGIT/r5r", subdir = "r-package")
```

@@

Note that the resulting `ttm` object only holds the travel time of 1043 
origin/destination pairs, even though the `points` data set passed both to 
`origins` and `destinations` argument contains 100 points. This is because out 
of the total 10000 possible trips between the supplied points, only 1043 could 
be completed within the specified restrictions. Removing any walking distance 
limits (by setting it to infinite) and increasing maximum trip duration 
accordingly results in a "complete" output:
